% Errata from Abstract Algebra, 2nd ed. by Grillet
% By John Peloquin
\documentclass[letterpaper,12pt]{article}
\usepackage{amsmath,amssymb,amsthm,enumitem,diagrams,fourier}

\newcommand{\sect}{\cap}
% TODO: replace with Grillet's symbol for normal subgroup
\newcommand{\normal}{\trianglelefteq}
\newcommand{\pres}[2]{\langle\,{#1}\mid{#2}\,\rangle}

% Meta
\title{Errata from \textit{Abstract Algebra}}
\author{John Peloquin}
\date{}

\begin{document}
\maketitle
\section*{Introduction}
This document contains errata from~\cite{grillet}. Positive line numbers count from the top of the page, while negative line numbers count from the bottom of the page. Displayed equations, diagrams, and figures are counted as single lines.

\section*{Chapter~I}
\begin{itemize}
\item p.~6, l.~-19: ``by Proposition~1.12'' should be deleted (because there is no such proposition).
\item p.~11, l.~-10: \(x_1=x_2=\cdots=x_m=-a\) should be \(x_1=x_2=\cdots=x_m=a\).
\item p.~18, l.~10: the end of proof symbol~``\qedsymbol'' should be deleted.
\item p.~21, l.~-5: ``4.16''~should be~``4.9''.
\item p.~23--4: in the statement and proof of Theorem~5.2, \(f\)~should be~\(\varphi\).
\item p.~24, l.~-13: ``5.1''~should be~``5.2''.
\item p.~24, l.~-11: \(a\in\ker p\)~should be~\(m\in\ker p\).
\item p.~25, l.~3: ``isomorphisms theorems'' should be ``isomorphism theorems''.
\item p.~26, l.~3: \(A\sect N\normal N\) should be \(A\sect N\normal A\).
\item p.~33, l.~3,5: \(\varphi\)~should be~\(\pi\).
\item p.~33, l.~3: \(F\)~should be~\(F_X\).
\item p.~33, l.~-10: \(\varphi\)~should be~\(\psi\).
\item p.~34, l.~3: the diagram should be
\begin{diagram}[nohug]
X	&\rTo^{\eta}	&F_X			&\rTo^{\pi}			&\pres{X}{R}\\
	&\rdTo<f		&\dDashto>{\varphi}	&\ldDashto>{\psi}	&\\
	&			&G				&				&
\end{diagram}
\item p.~40, l.~-5: the diagram should be the coproduct diagram
\begin{diagram}[nohug]
A	&\rTo^{\iota}		&A\amalg B		&\lTo^{\kappa}	&B\\
	&\rdTo<{\varphi}	&\dDashto>{\chi}	&\ldTo>{\psi}	&\\
	&				&G				&			&
\end{diagram}
\end{itemize}

\section*{Chapter~II}
\begin{itemize}
\item p.~45, l.~16: \(p_2^{k_2}\)~should be~\(p^{k_2}\).
\item p.~46, l.~7: ``since \((c^m)^k=1\) if and only if \(mn\)~divides~\(mk\), if and only if \(n\)~divides~\(k\)'' should be ``since \((c^n)^k=1\) if and only if \(mn\)~divides~\(nk\), if and only if \(m\)~divides~\(k\)''.
\item p.~47, l.~-14: ``every homomorphisms'' should be ``all homomorphisms''.
\item p.~48, l.~-12: \(G\)~should be~\(G_1\times G_2\times\cdots\times G_n\).
\item p.~50, l.~-17: ``inner automorphism'' has not yet been defined.
\item p.~52, l.~12,13: \(x_1x_2\cdots x_n\) should be \(x_1x_2\cdots x_m\).
\item p.~52, l.~19,21,22: \(\eta_n\)~should be~\(\eta_m\).
\item p.~53, l.~12: \(m\leqq k\) should be \(k\leqq m\).
\item p.~53, l.~15,17: \(\zeta_m\)~should be~\(\zeta_n\).
\item p.~55, l.~10: ``a subgroup of~\(G\)'' should be ``a subgroup~\(H\) of~\(G\)''.
\item p.~60, l.~-3: \(\sigma\tau x=x\tau\sigma x\) should be \(\sigma\tau x=x=\tau\sigma x\).
\item p.~61, l.~13: \(\gamma_A=(a,\sigma a,\ldots,\sigma^{k-1}a)\) should be \(\gamma_A=(a\ \sigma a\ \cdots\ \sigma^{k-1}a)\).
\item p.~69, l.~19: \(D_4\)~should be~\(D_6\).
\item p.~71, l.~-13: \(\{r_0,r_1\}\) should be \(\{r_0,r_2\}\).
\item p.~71, l.~-1: \(B_{i+1}\)~should be~\(B_{j+1}\).
\item p.~73, l.~11: ``\(T\normal ST\)'' should be deleted (because we already know that).
\item p.~74, l.~14: \(D_{\sigma(k-1)}\)~should be~\(D_{\sigma k-1}\).
\item p.~75, l.~17: we must assume \(i\ne k\).
\item p.~75, l.~-11: \(A\)~should be~\(A_n\).
\item p.~80, l.~8: \(E_1\cdots E_nM\) should be \(E_1\cdots E_n D\).
\item p.~81, l.~-11: \(Eu\)~should be~\(Ev\).
\item p.~81, l.~-9: ``8.4''~should be~``8.3''.
\item p.~82, l.~-15: \(PSL(2,2)\)~should be~\(PSL(2,3)\).
\item p.~85, l.~13: ``there are Sylow \(p\)-subgroups \(S\)~and~\(T\)'' should be ``there are distinct Sylow \(p\)-subgroups \(S\)~and~\(T\)''.
\item p.~89, l.~-6: \(g=c_1,\cdots,c_n\) should be \(g=c_1\cdots c_n\).
\item p.~89, l.~-7: \(G_k\)~should be~\(G^k\).
\item p.~91, l.~15: \(C(G/Z_k)\)~should be~\(Z(G/Z_k)\).
\item p.~95, l.~12: the end of proof symbol~``\qedsymbol'' should be deleted.
\item p.~100, l.~-12: \(rt\equiv 1\) should be \(rt\equiv t\).
\item p.~101, l.~-9: \(s_{j,k}s_{j+k-nl}\) should be \(s_{j,k}s_{j+k-n,l}\).
\item p.~102, l.~15: \(\prod_{c\in Q}s_{a,bc}\)~should be~\(\prod_{b,c\in Q}s_{a,bc}\).
\item p.~102, l.~-19: ``12.8''~should be~``12.6''.
\end{itemize}

% References
\begin{thebibliography}{0}
\bibitem{grillet} Grillet, Pierre~A. \textit{Abstract Algebra}, 2nd~ed., 1st~printing. Springer, 2007.
\end{thebibliography}
\end{document}
